\documentclass[../mthe-493-project-proposal.tex]{subfiles}

% Proposed Solution/Design: You will be dealing with Modelling and Design aspects in this section. Most of your design will be done on the model you produce. The theory you have researched will contribute to making a suitable model, and ultimately what design you do on this model. Include the tools (theory, processes, and/or techniques) you will use in your project (don’t forget to reference). Also, you need to consider Triple Bottom Line Factors, how they are relevant to your application and how they could influence your design. Try to be as quantitative as possible, and outline performance goals. Make sure the design aspect of your project is clear.
\begin{document}
    \chapter{Proposed Solution/Design}
    \label{ch:proposed-design}

    \section{Mathematical Model}
    % First paragraph: what is the focus of the research moving forward, based on section 2.0 of the problem definition?
    % - Cost function minimization in the context of a stochastic optimization problem
    % - Minimize the resource price to deploy a job such that a target completion time is not exceeded
    Following the modelling of the fundamental problem as a stochastic optimization problem in~\autoref{sec:mathematical-description}, a literature review of relevant work specific to both the general problem and the application problem of~\autoref{sec:application} will be conducted. The goal of this investigation is to determine if a general solution that minimizes \textit{resource price}~\eqref{eq:resource-price} given a target \textit{completion time}~\eqref{eq:completion-time} is possible, and if so, the conditions under which a solution is valid.
    
    % Second paragraph: where will development/refinement of the Application section of the mathematical model/problem definition proceed?
    % Just starting the next paragraph...
    If a general solution to the aforementioned problem does exist, the design and implementation of an algorithm that encapsulates said solution will follow. If not, then efforts will be put into the development of a heuristic solution. Due to the complex nature of the problem, it may be necessary to investigate and trial multiple algorithms and/or heuristic solutions.
    % Mike, finish this
    
    The final mathematical optimization framework must be implementable into an active network so that the orchestrator may rapidly employ it to optimally distribute any new job it is tasked with deploying. 
    %In order to rapidly minimize the effects of run-time and price in an implemented system, the orchestrator will need to use a minimization algorithm to find the best way to partition and allocate input sets. Values for $\mathbf{R}$, $\mathbf{P}$, and $\mathbf{A}$ can be measured dynamically and fed into the algorithm. Literature surrounding the minimization of cost functions on similarly defined networks will be reviewed in order to find and test algorithms that are well suited to this problem.
    

    \section{Design Implementation}
    \subsection{Existing Workflow}

    The edge computing resource allocation model will be implemented by leveraging  Kings Distributed Systems' Distributed Compute Protocol (DCP). The DCP is a framework for edge computing. The DCP is composed of a task scheduler, workers, and the protocol layer. A job that is to be computed using the DCP is broken up into discrete slices and stored in a simple data structure. A \emph{work} function is written and defines the computations to be performed on the data set. Work functions are paired with an input set of tasks and is then called a \emph{job}. Once the job is deployed, the workers request a subset of the job. The current way that the scheduler delegates these subsets, called \emph{tasks}, is in uniform chunks. The computational ability of the workers have no effect on the size of the task.

    \subsection{Cost and Constraints}
    \label{ssec:costs-and-constraints}

    The DCP workers consist of various personal computers out in the world and are compensated monetarily for doing work. Each worker has a normalized minimum price per unit of work, and each client of the DCP sets a price for a job that they are willing to pay. The scheduler handles the arbitration of matching jobs with workers that have a mutually agreeable fee. In production, there are different ways that the DCP is used, however the scope of this project constrains the setup which uses a finite, heterogeneous worker pool. This means that the number of workers is static, but the heterogeneity means that they have different computation power. This project will build functionality on top of the current DCP workflow to benchmark workers and distribute tasks based on time constraints. The optimization will be minimizing the cost of computing the job, given that the time to compute cannot exceed the upper bound. Methods of calculating the upper bounds and cost of workers will be provided, and thus are classified as assumptions.

    \subsection{New Workflow}
    \label{ssec:new-workflow}

    To implement the mathematical model in practice, additional functionality will sit on top of the existing framework. The scheduler interactions that would typically be initiated by user interaction will be managed by an orchestrator program. The orchestrator will send out a "benchmark job" to the worker pool, which is a simple job that will be used to determine the computation power of each worker. The worker will locally determine its upper bound and send this information back to the orchestrator. These inputs will feed into code that calculates task distributed based on the mathematical models, and then this information will be provided for the scheduler to leverage.
    
    At this point, the details of implementation for the application of DL, or more specifically PL, are not concrete. More research will have to be done on exactly how each edge device will have the requirements needed to run local training iterations, and how uniformization of any input parameters/hyperparameters can be guaranteed. In the event that this project cannot use the DCP's method of handling these dependencies, a more manual approach can be taken with the edge devices that will be used in our experimentation. 

    \subsection{Evaluation Metrics}

    The efficacy of the optimization model can be analyzed using many results. Since the primary objective of this project is to minimize the monetary cost of executing a job, it is the most significant result. However, completion time, staleness, and training accuracy must also be considered in the optimization model evaluation. Additionally, another metric for evaluation unrelated to the optimization problem will be the accuracy of task bench-marking.

    \section{Triple Bottom Line}
    The method of benchmarking the computational power mentioned in~\autoref{ssec:new-workflow} should not collect unnecessary data which could compromise the privacy of the devices in question. As such, the data collected during benchmarking will be modified to include only what is necessary to calculate the device's computational capabilities. In addition to minimizing the cost associated with having a worker work on a slice mentioned in~\autoref{ssec:costs-and-constraints}, the design will also need to consider the costs associated with benchmarking the workers despite it being an assumption. The additional computational power used could in result in negating the energy savings in using edge computing versus traditional computing.
\end{document}
