\documentclass[../mthe-493-project-proposal.tex]{subfiles}

% Team Members and Load Distribution/Assigned Tasks
\begin{document}
    \chapter{Team Members and Load Distribution/Assigned Tasks}
    \label{ch:team-load-distribution}

    \section{Bryan Hoang}
    \begin{itemize}
        \item Assisting team members with knowledge regarding the DCP. e.g., \begin{itemize}
                  \item Helping implement the model using the DCP by noting certain restrictions and features of the platform.
                  \item Helping deploy the application job on the DCP.
                  \item Helping clarify the mathematical model to fit the DCP's quirk's/behaviour.
              \end{itemize}
        \item Researching Triple Bottom Line Factors.
        \item Helping typeset deliverable documents for consistency in style.
    \end{itemize}

    \section{Jack Malloch}
    \begin{itemize}
        \item Researching distributed learning methods for application.
        \item Implementing all parallel learning code in the DCP.
        \item Evaluating and bench-marking distributed learning accuracy using application appropriate metrics. 
            \begin{itemize}
                \item i.e. mAP or Mean Average Precision for an object detection application.
            \end{itemize}
    \end{itemize}

    \section{Jared McGrath}
    \begin{itemize}
        \item Leading the mathematical modelling of the design problem.
        \item Abstracting the problem to applicable fields of math and finding useful theorems/methods to study the problem.
    \end{itemize}

    \section{Edan Parker}
    \begin{itemize}
        \item Designing and architecting the infrastructure in code.
        \item Writing documentation related to the infrastructure setup.
        \item Recording evaluation metrics and transforming output to charts.
    \end{itemize}

    \section{Michael Treagus}
    \begin{itemize}
        \item Working on the mathematical modelling of the design problem.
        \item Leading the implementation of the optimization calculations in code.
        \item Focusing on applying the math to the problem in a concrete way.
    \end{itemize}
\end{document}
