\documentclass[11pt]{meetingmins}

\setcommittee{MTHE 493 Group A2}

\setdate{2021-11-04}

\setpresent{
    Sara~A.~E.,
    Bryan~H.,
    Jack~M.,
    Edan~P.,
    Michael~T.,
    Jared~M.
}

% \absent{
%
% }

% \alsopresent{
%     Hossam~H.,
% }

\begin{document}
    \maketitle

    \section{Minutes}
    \begin{items}
        \item Merits of starting off with a simple job to make modelling and estimations of timings simpler before moving onto using PL as the job.
        \begin{itemize}
            \item Is using DCP worth it (network costs more uncertain?).
            \item Duncan's model naively estimates networking timings. Can have room for improvement (may not have enough time to improve this significantly).
            \item \textbf{Whatever is decided, keep timeline in mind.}
            \item Because of that, probably not necessary to use a simple model initially if we lose time unnecessarily.
            \item If something like this is brought up again, come to Sarah with a plan (e.g., who, when, how).
        \end{itemize}
        \item Clarify team roles/timelines and considering time for testing.
    \end{items}

    \section{Action Items}
    \begin{items}
        \item For the group, create a concrete agenda for future meetings including: what has been done, what are our plans.
        \item By next week, the group will set up a repository for the project and continue to develop the mathematical model (i.e., investigating branches of math for network modelling).
    \end{items}

    \vspace{1em}

    \nextmeeting{2021-11-13, 17:00}
\end{document}
